model_fit

### 2025-12-07 Slides.Rmd
slides update2

## Discussion: Business Impact (Slide 13)
* **Discuss:** How the **chosen model** (Balancing performance and interpretability) can lead to **cost savings** and **higher ROI** for future campaigns.
* **Discuss:** Briefly touch upon **regulatory/ethical implications** in banking and the need to justify predictions (further supporting the value of interpretability).
* **Image/Plot Idea:** A currency symbol or a bar chart showing the conceptual increase in ROI due to better targeting.

## Discussion: Limitations & Future Work (Slide 14)
* **Discuss:** Acknowledge limitations, such as not using **time-series analysis** or fully accounting for the dependency of the 'duration' feature.
* **Discuss:** Suggest future improvements: Exploring advanced techniques like **resampling methods** (SMOTE) to handle imbalance better or trying **Deep Learning** models.
* **Image/Plot Idea:** A bulleted list of 2-3 **future research questions** (e.g., Time-Series, SMOTE, Deep Learning).

>>>>

## Discussion: Business Impact (Slide 13)  #MUSSA
* **Discuss:** How the **chosen model** (Balancing performance and interpretability) can lead to **cost savings** and **higher ROI** for future campaigns.
* **Discuss:** Briefly touch upon **regulatory/ethical implications** in banking and the need to justify predictions (further supporting the value of interpretability).
* **Image/Plot Idea:** A currency symbol or a bar chart showing the conceptual increase in ROI due to better targeting.

## Discussion: Limitations & Future Work (Slide 14)  #MUSSA
* **Discuss:** Acknowledge limitations, such as not using **time-series analysis** or fully accounting for the dependency of the 'duration' feature.
* **Discuss:** Suggest future improvements: Exploring advanced techniques like **resampling methods** (SMOTE) to handle imbalance better or trying **Deep Learning** models.
* **Image/Plot Idea:** A bulleted list of 2-3 **future research questions** (e.g., Time-Series, SMOTE, Deep Learning).

### 2025-12-07 model_fit.Rmd
slides update2

view(coef_df %>%  filter(`Pr(>|z|)`< 0.01))
```

@@

*Standard raw logistic reg (without tuning)*

```{r}
glm_out <- glm(y ~ ., data = bank_full, family = binomial)
summary(glm_out)
```

Discuss accuracy (cv test error) and amount of parameters

```{r}
glm.full.cv <- glm(initial_formula, data = data, family = binomial, x = TRUE)

cv.error.full <- cv.glm(data, glm.full.cv, K = 5)$delta[2]
length(coef(glm.full.cv))
```

This model is complex due to the large number of dummy variables. The CV test error provides an estimate of how well this complexity generalizes to new, out of sample data. If the CV error is significantly higher than the training error, the model is likely overfitting

>>>>

sample(coef_df %>%  filter(`Pr(>|z|)`< 0.01))
```

@@
